### 2025-04-23 notes/ms.tex
maximum principle

\end{claim}
\item \textit{\textbf{Weierstrass data}}:
	\begin{enumerate}
	\item A complex structure \(J\) on \(\Sigma\).
	\item \(\alpha_1,\ldots,\alpha_n \in \Gamma(\Sigma_J,\omega_\Sigma)\) such that
		\[\sum_{k=1}^n(\alpha_k)^2=0 \in \Gamma(\Sigma_J,\omega_\Sigma^{\otimes 2})\]
	\item \(\forall \gamma \in H_1(\Sigma,\mathbb{R})\) s.t. \(\forall k=1,\ldots,n\),
		\[\operatorname{Re} \int_\gamma \alpha_k=0\]
		``Global conditions on periods"
	\end{enumerate}
\begin{claim}\leavevmode
Weierstrass data \(\iff\) Minimal surfaces with
\[\vec{X}(p)=\operatorname{Re}\int_{p_0}^p \vec{\alpha}.\]
\end{claim}
\end{enumerate}

\subsection{Outline of the proof of E. Hopf. theorem}

\begin{thm}[E. Hopf]\leavevmode
For any \((M,g)\), harmonic functions satisfy \textit{\textbf{maximum principle}}. That is, any harmonic function \(f:U \to \mathbb{R}\) for \(U\) connected and open, if \(\exists p \in U\) that is a local maximum or local minimum, then \(f\) is constant on \(U\).
\end{thm}

\begin{proof}\leavevmode
\begin{enumerate}[label=\textbf{Step \arabic*}]
\item Make sure you can pick a ``Referencial geodésico" about every point of \(M\). This is an orthonormal frame \(\{E_i\} \subset \mathfrak{X}(U)\), where \(p \in U\) such that \(\Big(\nabla_{E_i}E_j\Big)_p=0\). This frame can be obtained by taking geodesic coordinates at the point, an orthonormal base \(\{e_i\}\) of \(T_pM\), and taking the parallel transport of the vectors \(e_i\) along radial geodesics emanating from \(p\). (\cite{doc}, Cap. III, Ex. 7.)

\item Prove that \[di_X \operatorname{Vol}=\operatorname{div}X \operatorname{Vol}\] (\cite{doc} Cap. III, Ex. 11.) To do this pick a Geodesic frame \(E_i\) and its dual coframe \(\varepsilon^i\), i.e. satisfying \(\varepsilon^i(E_j)=\delta_{ij}\). Then \(\operatorname{Vol}=\varepsilon^1 \wedge \ldots \wedge \varepsilon^n\). Then for any \(X=X^iE_i \in \mathfrak{X}(U)\),
	\begin{align*}
	i_X\operatorname{Vol}&=\varepsilon^1\wedge\ldots\wedge\varepsilon^n(X^iE_i,\cdot,\ldots,\cdot)=X^i\varepsilon^1\wedge\ldots\wedge\varepsilon^n(E_i,\cdot,\ldots,\cdot)
	\end{align*}
	How to compute that? Recall that for top-forms we have
	\[\varepsilon^1\wedge\ldots\wedge\varepsilon^n(Z_1,\ldots,Z_n)=\det(\varepsilon^i(Z_j))\]
	so for example if \(n=3\)
	\begin{align*}\varepsilon^1\wedge \varepsilon^2\wedge\varepsilon^3(E_1,Z_2,Z_3)&=\begin{vmatrix} \varepsilon^1(E_1)&\varepsilon^1(Z_2) &\varepsilon^1(Z_3)\\
\varepsilon^2(E_1)&\varepsilon^2(Z_2)&\varepsilon^2(Z_3)\\
\varepsilon^3(E_1)&\varepsilon^3(Z_2)&\varepsilon^3(Z_3)
	\end{vmatrix}=\begin{vmatrix} 1&\varepsilon^1(Z_2) &\varepsilon^1(Z_3)\\
0&\varepsilon^2(Z_2)&\varepsilon^2(Z_3)\\
0&\varepsilon^3(Z_2)&\varepsilon^3(Z_3)
	\end{vmatrix}\\
	&=\varepsilon^2(Z_2)\varepsilon^3(Z_3)-\varepsilon^2(Z_3)\varepsilon^3(Z_2)=\varepsilon^2\wedge\varepsilon^3(Z_2,Z_3),\\
	\varepsilon^1\wedge\varepsilon^2\wedge\varepsilon^3(E_2,Z_2,Z_3)&=\begin{vmatrix} 0&\varepsilon^1(Z_2) &\varepsilon^1(Z_3)\\
1&\varepsilon^2(Z_2)&\varepsilon^2(Z_3)\\
0&\varepsilon^3(Z_2)&\varepsilon^3(Z_3)
	\end{vmatrix}=-\varepsilon^1\wedge\varepsilon^3(Z_2,Z_3)
	\end{align*}
and so on. When we sum over all \(i\), we get
\[X^i\varepsilon^1\wedge\ldots\wedge\varepsilon^n(E_i,\cdot,\ldots,\cdot)=\sum_{i}(-1)^{i+1}X^i\varepsilon^1\wedge\ldots\wedge\widehat{\varepsilon^i}\wedge\ldots\wedge\varepsilon^n.\]
Now take exterior derivative of that, we get
\begin{align*}
d i_X\operatorname{Vol}&=\sum_i(-1)^{i+1}(dX^i)\wedge\varepsilon^1\wedge\ldots\wedge\widehat{\varepsilon^i}\wedge\ldots\wedge\varepsilon^n\\
&+\sum_{i}(-1)^{i+1}X^i\wedge d(\varepsilon^1\wedge\ldots\wedge\widehat{\varepsilon^i}\wedge\ldots\wedge\varepsilon^n)\end{align*}
And then the first term actually is
\begin{align*}
\sum_i(-1)^{i+1}E_jX^i\varepsilon^j\wedge\varepsilon^1\wedge\ldots\wedge\widehat{\varepsilon^i}\wedge\ldots\wedge\varepsilon^n&=E_iX^i\operatorname{Vol}
\end{align*}
while the second term vanishes because look,
\begin{align*}d \varepsilon^i(E_j,E_k)&=E_j\varepsilon^i(E_k)-E_k\varepsilon^i(E_j)-\varepsilon^i([E_j,E_k])\\
&=-\varepsilon^i(\nabla_{E_j}E_k-\nabla_{E_k}E_j)\qquad \text{torsion!} \end{align*}
which vanishes at \(p\) because we said that this geodesic frame would have vanishing Christoffel symbols at \(p\). So we conclude:
\[di_X \operatorname{Vol}=E_iX^i\operatorname{Vol}\]

Now you just have to think what is divergence: divergence is \(\operatorname{div}X\overset{\operatorname{def}}{=}\operatorname{tr}(v \mapsto \nabla_vX)\). So
\begin{align*}
\operatorname{div}X&=\sum_{i}\left<\nabla_{E_i}X^jE_j,E_i\right>=\sum_{i}\left<E_iX^jE_j,E_i\right>+X^j\left<\nabla_{E_i}E_j,E_i\right>\\
&=\sum_i \left<E_iX^jE_j,E_i\right>=\sum_iE_iX^j\left<E_j,E_i\right>=E_iX^i
\end{align*}
again using that we are a geodesic frame with vanishing covariant derivative at \(p\).

\item (This is the next exercise in \cite{doc}… *in progress*)
\end{enumerate}
\end{proof}

>>>>

\end{claim}
\item \textit{\textbf{Weierstrass data}}:
	\begin{enumerate}
	\item A complex structure \(J\) on \(\Sigma\).
	\item \(\alpha_1,\ldots,\alpha_n \in \Gamma(\Sigma_J,\omega_\Sigma)\) such that
		\[\sum_{k=1}^n(\alpha_k)^2=0 \in \Gamma(\Sigma_J,\omega_\Sigma^{\otimes 2})\]
	\item \(\forall \gamma \in H_1(\Sigma,\mathbb{R})\) s.t. \(\forall k=1,\ldots,n\),
		\[\operatorname{Re} \int_\gamma \alpha_k=0\]
		``Global conditions on periods"
	\end{enumerate}
\begin{claim}\leavevmode
Weierstrass data \(\iff\) Minimal surfaces with
\[\vec{X}(p)=\operatorname{Re}\int_{p_0}^p \vec{\alpha}.\]
\end{claim}
\end{enumerate}
\subsection{Maximum principle}

\begin{thing7}{Maximum principle}[E. Hopf]\leavevmode
\textbf{(Class statement.)} For any \((M,g)\), harmonic functions satisfy \textit{\textbf{maximum principle}}: any harmonic function \(f:U \to \mathbb{R}\) for \(U\) connected and open, if \(\exists p \in U\) that is a local maximum or local minimum, then \(f\) is constant on \(U\).

We shall show Do Carmo's version that \(f\) \textit{\textbf{subharmonic}}, i.e. \(\Delta f\geq 0\), on \(M\) compact connected \(\implies\) \(f\) constant. (This is Exercise 12, Chapter III, \cite{doc}, and all steps are just other exercises from the chapter of Geodesics :))
\end{thing7}

\begin{proof}\leavevmode
\begin{enumerate}[label=\textbf{Step \arabic*}]
	\item \textbf{(Exercise 7, Chapter III of  \cite{doc}.)} Make sure you can pick a \textit{\textbf{referencial geodésico}} about every point of \(M\). This is an orthonormal frame \(\{E_i\} \subset \mathfrak{X}(U)\), where \(p \in U\) such that \(\Big(\nabla_{E_i}E_j\Big)_p=0\). This frame can be obtained by taking geodesic coordinates at the point, an orthonormal base \(\{e_i\}\) of \(T_pM\), and taking parallel transport of the vectors \(e_i\) along radial geodesics emanating from \(p\). This immediately ensures that \(E_i\) is orthonormal since parallel transport preserves angles.

		To check that Christoffel symbols vanish at \(p\) we do as follows. (This is actually a basic fact about geodesic coordinates, see \cite{ler} Prop. 5.24.) Take a random vector \(v \in T_pM\) and its geodesic \(\gamma_v(t)=\operatorname{exp}_p(tv)\). I drop the subindex \(v\) for the next computations for the next computations. Then (this is Florit way of using covariant derivative along a curve; it's the \textit{\textbf{pullback}} or \textit{\textbf{induced connection}} \(\nabla^{\gamma}\)):
		\begin{align*}
			0&=\nabla_{\frac{d}{dt}}^{\gamma}\gamma'=\nabla^{\gamma}_{\frac{d}{dt}}v^i(E_i\circ \gamma)
		\end{align*}
		where the \(v=(v^1,\ldots,v^n)\). Indeed: this is very silly but, since the coordinate chart of geodesic coordinates is \(\operatorname{exp}_p^{-1}\), the coordinate representation of \(\gamma\) in this chart is as simple as
	\[\hat{\gamma}(t)=(\underbrace{\varphi}_{\text{chart}} \circ \gamma)(t)=\operatorname{exp}_p^{-1} \operatorname{exp}_p(tv)=tv.\]
And the composition \(E_i \circ \gamma\) just means that we take our local frame \textit{along \(\gamma\)}. Continue:
		\begin{align*}
		&=v^i\nabla^{\gamma}_{\frac{d}{dt}}E_i\circ\gamma=v^i\nabla_{\gamma_{v,*} \frac{d}{dt}}E_i\\&=v^i\nabla_{v^jE_j}E_i=v^iv^j\nabla_{E_j}E_i\\&=v^iv^j\Gamma_{ji}^kE_k
		\end{align*}
along \(\gamma\). Now choose \(v=e_1\). You get \(\Gamma_{11}^k=0\) for all \(k\) along \(\gamma_{e_1}\). Now choose \(v=e_2\), then \(\Gamma_{22}^k=0\) along \(\gamma_{e_2}\), so at least at \(p\) they both vanish. And now choose \(v=e_1+e_2\). You get
\begin{align*}
	0=(v^1)^2 \cancelto{0}{\Gamma_{1 1}^k}+v^1v^2 \Gamma_{1 2}^k+v^2v^1\Gamma_{2 1}^k+(v^2)^2\cancelto{0}{\Gamma_{2 2}^k}
\end{align*}
So \(\Gamma_{12}^k=0\) since Levi-Civita is torsion-free, i.e. symmetric. And so on. So the all Christoffel symbols vanish at the same time at \(p\).
\item \textbf{(Exercise 11, Chapter III of  \cite{doc}.)} Prove that \[di_X \operatorname{Vol}=\operatorname{div}X \operatorname{Vol}\]
	To do this first recall that \textit{\textbf{divergence}} and \textit{\textbf{trace}} are
	\begin{align*}\operatorname{div}X&:=\operatorname{tr}(v \mapsto \nabla_vX)\\ \\
		\operatorname{tr}(T)&:=\sum_i\left<TE_i,E_i\right>, \qquad T\in \operatorname{End}(V), E_i\text{ orthonormal frame} \end{align*}
	Now pick a Geodesic frame \(E_i\) and its dual coframe \(\varepsilon^i\), i.e. satisfying \(\varepsilon^i(E_j)=\delta_{ij}\). Then \(\operatorname{Vol}=\varepsilon^1 \wedge \ldots \wedge \varepsilon^n\). Then for any \(X=X^iE_i \in \mathfrak{X}(U)\),
	\begin{align*}
	i_X\operatorname{Vol}&=\varepsilon^1\wedge\ldots\wedge\varepsilon^n(X^iE_i,\cdot,\ldots,\cdot)=X^i\varepsilon^1\wedge\ldots\wedge\varepsilon^n(E_i,\cdot,\ldots,\cdot)
	\end{align*}
	How to compute that? Recall that for top-forms we have
	\[\varepsilon^1\wedge\ldots\wedge\varepsilon^n(Z_1,\ldots,Z_n)=\det(\varepsilon^i(Z_j))\]
	so for example if \(n=3\)
	\begin{align*}\varepsilon^1\wedge \varepsilon^2\wedge\varepsilon^3(E_1,Z_2,Z_3)&=\begin{vmatrix} \varepsilon^1(E_1)&\varepsilon^1(Z_2) &\varepsilon^1(Z_3)\\
\varepsilon^2(E_1)&\varepsilon^2(Z_2)&\varepsilon^2(Z_3)\\
\varepsilon^3(E_1)&\varepsilon^3(Z_2)&\varepsilon^3(Z_3)
	\end{vmatrix}=\begin{vmatrix} 1&\varepsilon^1(Z_2) &\varepsilon^1(Z_3)\\
0&\varepsilon^2(Z_2)&\varepsilon^2(Z_3)\\
0&\varepsilon^3(Z_2)&\varepsilon^3(Z_3)
	\end{vmatrix}\\
	&=\varepsilon^2(Z_2)\varepsilon^3(Z_3)-\varepsilon^2(Z_3)\varepsilon^3(Z_2)=\varepsilon^2\wedge\varepsilon^3(Z_2,Z_3),\\
	\varepsilon^1\wedge\varepsilon^2\wedge\varepsilon^3(E_2,Z_2,Z_3)&=\begin{vmatrix} 0&\varepsilon^1(Z_2) &\varepsilon^1(Z_3)\\
1&\varepsilon^2(Z_2)&\varepsilon^2(Z_3)\\
0&\varepsilon^3(Z_2)&\varepsilon^3(Z_3)
	\end{vmatrix}=-\varepsilon^1\wedge\varepsilon^3(Z_2,Z_3)
	\end{align*}
and so on. When we sum over all \(i\), we get
\[X^i\varepsilon^1\wedge\ldots\wedge\varepsilon^n(E_i,\cdot,\ldots,\cdot)=\sum_{i}(-1)^{i+1}X^i\varepsilon^1\wedge\ldots\wedge\widehat{\varepsilon^i}\wedge\ldots\wedge\varepsilon^n.\]
\begin{thing7}{Meta-remark}[Victor and dani discussed Koszul complex yesterday]\leavevmode
	Here! This is nervously similar to the definition of Koszul differential. Looks like: fix a vector field, contract the volume form and then just keep contracting with that vector field. We should end up with a map from 1-forms to \(\mathbb{R}\)… but what is that map in this case? In Koszul complex this map was the \textit{starting point} of the construction…
\end{thing7}

Now take exterior derivative of that, we get
\begin{align*}
d i_X\operatorname{Vol}&=\sum_i(-1)^{i+1}(dX^i)\wedge\varepsilon^1\wedge\ldots\wedge\widehat{\varepsilon^i}\wedge\ldots\wedge\varepsilon^n\\
&+\sum_{i}(-1)^{i+1}X^i\wedge d(\varepsilon^1\wedge\ldots\wedge\widehat{\varepsilon^i}\wedge\ldots\wedge\varepsilon^n)\end{align*}
And then the first term actually is
\begin{align*}
\sum_i(-1)^{i+1}E_jX^i\varepsilon^j\wedge\varepsilon^1\wedge\ldots\wedge\widehat{\varepsilon^i}\wedge\ldots\wedge\varepsilon^n&=E_iX^i\operatorname{Vol}
\end{align*}
while the second term vanishes because look,
\begin{align*}d \varepsilon^i(E_j,E_k)&=\underbrace{E_j\varepsilon^i(E_k)-E_k\varepsilon^i(E_j)}_{\text{must vanish}}-\varepsilon^i([E_j,E_k])\\
&=-\varepsilon^i(\nabla_{E_j}E_k-\nabla_{E_k}E_j)\qquad \text{torsion!} \end{align*}
which vanishes at \(p\) because we said that this geodesic frame would have vanishing Christoffel symbols at \(p\). So we conclude:
\[di_X \operatorname{Vol}=E_iX^i\operatorname{Vol}\]

Now you just have to think what is divergence:
\begin{align*}
\operatorname{div}X&=\sum_{i}\left<\nabla_{E_i}X^jE_j,E_i\right>=\sum_{i}\left<E_iX^jE_j,E_i\right>+X^j\left<\nabla_{E_i}E_j,E_i\right>\\
&=\sum_i \left<E_iX^jE_j,E_i\right>=\sum_iE_iX^j\left<E_j,E_i\right>=E_iX^i
\end{align*}
again using that we are a geodesic frame with vanishing covariant derivative at \(p\).

	\item \textbf{(Exercise 9(b), Chapter III of  \cite{doc}.)} You realise that
	\[\Delta(fg)=f \Delta g + g \Delta f+2\left<\nabla f,\nabla g\right>.\]
	Recall that \textit{\textbf{Laplacian}} and \textit{\textbf{gradient}} are
	\[\Delta f:=\operatorname{div} \nabla f\qquad \left<\nabla f,X\right>:=dfX=Xf.\]
	So this equality is just a computation no problem, I'll say how it starts. For any \(X \in \mathfrak{X}(M)\),
	\begin{align*}
	\left<\nabla(fg),X\right>&=X(fg)=fXg+gXf=f\left<\nabla g,X\right>+g\left<\nabla f,X\right>.
	\end{align*}
	which says that	\begin{align*}\nabla(fg)&=f \nabla g+g \nabla f\end{align*}
	So, for an orthonormal frame \(E_i\)
	\begin{align*}\Delta(fg)=\operatorname{div} \nabla(fg)&=\sum_i\left<\nabla_{E_i}(f \nabla g+g \nabla f),E_i\right>
	\end{align*}
	Then use Leibniz rule and definition of gradient, you get there.

\item \textbf{(Exercise 12, Chapter III of  \cite{doc}.)} To prove the theorem for subharmonic functions first we show that in fact they are harmonic via step 2 on \(X:= \nabla f\) and Stokes:
	\[\int_M \Delta f \operatorname{Vol}=\int_M \operatorname{div}X \operatorname{Vol}=\int_M d(i_X \operatorname{Vol})=\int_{\partial M}i_X \operatorname{Vol}=0\]
meaning that the non-negative function \(\Delta f\) is in fact 0, i.e. \(f\) is harmonic. Now we do it again for \(X:=\nabla(f^2/2)\):
	\[\int_M \Delta(f^2/2)\operatorname{Vol}=\int_M d(i_X \operatorname{Vol})=\int_{\partial M}i_X \operatorname{Vol}=0\]
	And then apply step 3:
	\[0=\int_M \Delta(f^2/2)\operatorname{Vol}=\int_M f \Delta f \operatorname{Vol}+\int_M \left<\nabla f,\nabla f\right>\operatorname{Vol}\]
First one vanishes because \(f\) is harmonic, so second one is zero which says \(f\) is constant!
\end{enumerate}
\end{proof}

\bibliography{bib.bib}

\begin{enumerate}
\item Proof using isothermal coordinates that laplacian \(\Delta X\) where \(X: \Sigma \to \mathbb{R}^n\) is orthogonal to the embedded \(\Sigma\). Recall that \(\Delta X\) is just taking laplacian of every coordinate. But then you are using that  \(X\) goes to \(\mathbb{R}^n\). So question is how to generalize this to some other Riemannian manifold.
\end{enumerate}

Here's the notes crafted with lots of help of GPT:

\section*{Weierstrass Data}

\begin{enumerate}
    \item A complex structure \(J\) on \(\Sigma\).
    \item \(\alpha_1,\ldots,\alpha_n \in \Gamma(\Sigma_J,\omega_\Sigma)\) such that
    \[
    \sum_{k=1}^n(\alpha_k)^2=0 \in \Gamma(\Sigma_J,\omega_\Sigma^{\otimes 2})
    \]
    \item \(\forall \gamma \in H_1(\Sigma,\mathbb{R})\) s.t. \(\forall k=1,\ldots,n\),
    \[
    \operatorname{Re} \int_\gamma \alpha_k=0
    \]
    ``Global conditions on periods''
\end{enumerate}

Notice that \(|\vec{\varphi}(p)| > 0\) so that \(\vec{\varphi} \neq 0\), so you can take its class \([\vec\varphi(z)] \in \mathbb{P}(\mathbb{C}^n)\), which is in fact an element of the quadric
\[
\sum (\varphi^\mu)^2 = 0
\]
and then guess what: we have a map \(\Sigma \to Q\), that’s the quadric, but in fact Sergey showed earlier that the Gauss map \(\Sigma \to \mathrm{Gr}_+(2,\mathbb{R}^n)\), where in fact \(\mathrm{Gr}(2,\mathbb{R}^n)\) is a quadric, and it turns out that the construction above \emph{is} the Gauss map!

Now he takes an invertible holomorphic function \(F(z) \in \mathcal{O}^*(\Sigma)\)

The point is that \(\lambda = |F(z)|\) is the conformal factor, i.e. the new surface with the \(F\) is conformal to the old one by \(\lambda\).

\textbf{Important example:} \(F(z) = e^{i\theta}\)

\textbf{Definition:} Surfaces
\[
X_\theta(p) = \operatorname{Re} \left( e^{i\theta} \int_{p_0}^p \vec{\varphi}(z)\,dz \right)
\]
are called the \textbf{associated family}, and \(\theta = \pi/2\): conjugate surface.

\textbf{Example:} Helicoid is conjugate to catenoid.
